\section{Crazy Eights Game Logic}

\subsection{Crazy Eights Class}

\subsubsection{Refill deck}
Fills the deck with the discarded cards.

\subsubsection{Deck deck}
    Object deck which holds an array of 52 cards.

\subsubsection{enum Suit}
    Enumeration to represent the 4 suits: Hearts, Spades, Clubs, and Diamonds.

\subsubsection{int turnID}
    Variable to hold turn number for use in game logic.

\subsubsection{Suit currentSuit}
    Variable to hold current playable suit of the game.  Allows for 8s cards (wildcards) to switch the current playable suit.
    
\subsubsection{bool isPlayerTurn}
    flag that will switch depending on if you are allowed to make a move.

\subsubsection{int playerScore}
    variable to hold the final score of the winning player.
    
\subsubsection{start Round Function}
    Deal 5 Cards, decide who plays fist.
    
\subsubsection{deal card function}
    This function gives players appropriate number of cards at the beginning of each game.
\subsubsection{update Player Score }
    count cards for each player and assign an appropriate score.
\subsubsection{determine next turn}
    This function will figure out who makes the next turn.
\subsubsection{check for win condition}
    This function will check to see if a player has won the game.

\subsection{Deck class}

\subsubsection{Card[] cards}
    a vector of 52 cards.

\subsection{Discard pile class}
vector of cards.

\subsubsection{void shuffle()}
    shuffles the deck.
    

\subsection{Card Class}

\subsubsection{int cardRank}
    integer that represents a value for a card.
    
\subsubsection{Suit suit}
    Variable for the card to represent 1 of the 4 suits: Hearts, Spades, Clubs, and Diamonds.
    
\subsubsection{bool discarded}
    This indicates whether a card has been discarded or played in a game.
    
\subsubsection{bool validMove}
    checks to make sure a move is valid


